Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-11-16 special-issue-ci/Response to reviewers.tex

We thank the reviewer for the comment. The only reason why JavaScript
was chosen was because it is the only language that is native to the
browser, allowing to carry out precisely this kind of experiments
where the user is invited to click on an URL and start giving CPU to
it. Although there are many other volunteer frameworks, written in
other languages, that a priori would offer a higher performance, the
key is that they would {\em while they are running}, that is, as soon
as it has been installed, the user has decided to fire it up, and it
does not affect the performance in the rest of the system, which is a
concern in this kind of systems. We have performed speed tests on
JavaScript and other compiled languages resulting that, in fact,
JavaScript uses a JIT compiler that provides a good performance; we
have published these tests as an open access technical report.

JavaScript is probably the most popular language nowadays, and this
has inspired the appearance of many compilers, so that the fitness
function can, in fact, be written in any language and compiled to
JavaScript, as is shown in this list:
\url{https://github.com/jashkenas/coffeescript/wiki/list-of-languages-that-compile-to-js}. This
has also been added to the text.

In a nutshell, what we are saying is that, as is proven in the paper,
a JavaScript application, running in the browser, can gather in
seconds dozens of users. That would be, in practice, impossible with
other kind of native clients, who would have to download and maybe
compile the application, losing many seconds or minutes for the
optimization problem that has to be solved.

These facts, along the explanations, have now been added to the first
paragraph of the {\em Description of the system} section, as well as
to the introduction.

@@

\begin{quote}
The paper organization is not clear. Some comments about this:
- The title "Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed
Evolutionary Computation" seems to suggest that the volunteers run in the cloud, but that is not the case:
the server run in the cloud and the volunteers do in the browsers of
common PCs and laptops.
\end{quote}

That is correct. We just used {\em cloud} in a relatively informal
sense because they are available as in a cloud for running the
experiment. That is, from the point of view of the person running the
experiment, there is a {\em cloud} out there running your experiments,
which is actually run by volunteers in their browsers. We went to the
original aception of ``cloud'' as a ``network'' more than the more
precise and technical aception used today.

We have added this explanation to the first paragraph in the
conclusions; we hope this makes our intention clearer, but we can also
eliminate that part of the title if the reviewer think it is
necessary.

\begin{quote}
- The paper abstract does not properly summarize the paper contents. It says that "That is why in this
paper we present NodIO, a client-server architecture for distributed evolutionary algorithms !", but there
are two versions of the architecture, as stated later in the conclusions: "In this paper two versions of a
client-server architecture for volunteer and distributed evolutionary !". That second version is neither
commented in the introduction.
\end{quote}

In fact {\sf NodIO} is a framework that can be used to generate
different client-server architectures. This has been clarified in the
abstract and conclusions section.

\begin{quote}
- According the last paragraph of the introduction, ``Then, a detailed description of the proposed system is
presented in Section III, followed by the experiments and obtained results in Section IV.", but Section IV
does not only contains experimental result but also the full description of the second version of the
architecture.
Summarizing the review, the authors should provide a convincing example showing the advantages of
their proposal. As presented, the paper is a proof of concept of a system that seems difficult to be used
by the researchers needing high computational resources to run an evolutionary algorithm to solve a realworld
problem.
\end{quote}

### 2015-11-16 special-issue-ci/Response to reviewers.tex

We have added this explanation to the first paragraph in the
conclusions; we hope this makes our intention clearer, but we can also
eliminate that part of the title if the reviewer think it is
necessary.

\begin{quote}
- The paper abstract does not properly summarize the paper contents. It says that "That is why in this
paper we present NodIO, a client-server architecture for distributed evolutionary algorithms !", but there
are two versions of the architecture, as stated later in the conclusions: "In this paper two versions of a
client-server architecture for volunteer and distributed evolutionary !". That second version is neither
commented in the introduction.
\end{quote}

In fact {\sf NodIO} is a framework that can be used to generate
different client-server architectures. This has been clarified in the
abstract and conclusions section.

\begin{quote}
- According the last paragraph of the introduction, ``Then, a detailed description of the proposed system is
presented in Section III, followed by the experiments and obtained results in Section IV.", but Section IV
does not only contains experimental result but also the full description of the second version of the
architecture.
\end{quote}

You are absolutely right. We have corrected that paragraph to include
the actual contents of the paper.

\begin{quote}
Summarizing the review, the authors should provide a convincing example showing the advantages of
their proposal. As presented, the paper is a proof of concept of a system that seems difficult to be used
by the researchers needing high computational resources to run an evolutionary algorithm to solve a realworld
problem.
\end{quote}

### 2015-11-16 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
Including a better description of the real structure of the paper
This was oversight on our part. Closes #34

The rest of the paper is organized as follows: Next we present the
state of the art (Section \ref{sec:soa}) in web-based distributed
computation systems along with attempts to predict and model its behavior. 
Then, a detailed description of the proposed system is presented
in Section \ref{sec:description}, followed by the experiments and 
results obtained in Section \ref{sec:experiments}.
Finally, conclusions and future lines of work are presented in Section
\ref{sec:conclusion}.

@@

\section{{\sf NodIO-W$^2$}, a Web Worker-based architecture}

>>>>

The rest of the paper is organized as follows: Next we present the
state of the art (Section \ref{sec:soa}) in web-based distributed
computation systems along with attempts to predict and model its behavior. 
Then, a detailed description of the proposed system is presented
in Section \ref{sec:description}, followed by the baseline experiments
in Section \ref{sec:experiments} and experiments using a new client
architecture that uses web workers in Section \ref{sec:w2}.
Finally, conclusions and future lines of work are presented in Section
\ref{sec:conclusion}.

@@

\section{{\sf NodIO-W$^2$}, a Web Worker-based architecture}
\section{sec:w2}
